Amberson Towers <br/> Condominum Council" # only for pdf output

### 2022-02-09 DraftRules.Rmd
Even for link errors - learnin gow Gitpages handles links

---
title: "Amberson Towers Condominum Council" # only for pdf output
subtitle: "Rules & Regulations" # only for html output
author: "Draft by Governance Committee"
date: "`r Sys.Date()`"
output:
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

>>>>

---
title: "Amberson Towers <br/> Condominum Council" # only for pdf output
subtitle: "Rules & Regulations" # only for html output
author: "Draft by Governance Committee"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
bibliography: skeleton.bib
link-citations: yes
---
